Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added GLAD/EDGI employment prepan graph

>>>>

##Employment
###Prepan

```{r GLAD/EDGI employment prepan}

GLAD.prepan %>% 
  ggplot(aes(x = employment_prior_covid)) +
  geom_bar(fill = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
